\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2011-11-18 doc/USER_MANUAL/manual_SPECFEM3D.tex
fixed missing \eg
updated citations in manual (Ch 11)

\newcommand{\nexxi}{\mbox{\texttt{NEX\_XI\/}}}
\newcommand{\nexeta}{\mbox{\texttt{NEX\_ETA\/}}}
\newcommand{\nprocxi}{\mbox{\texttt{NPROC\_XI\/}}}
\newcommand{\nproceta}{\mbox{\texttt{NPROC\_ETA\/}}}
\newcommand{\nchunks}{\mbox{\texttt{NCHUNKS\/}}}

@@

Whatever misfit function you use for the tomographic inversion \citep[several examples in][]{Tromp2005}, you will weight the sensitivity kernels with measurements. Furthermore, you will use as many measurements (stations, components, time windows) as possible per event; hence, we call these composite kernels ``event kernels,'' which are volumetric fields representing the gradient of the misfit function with respect to one of the variables (\eg $V_{\rm s}$). The basic features of an adjoint-based tomographic inversion were illustrated in \citet{Tape2007} using a conjugate-gradient algorithm; there are dozens of versions of gradient-based inversion algorithms that could alternatively be used. The tomographic inversion of \citet{Tape2009,Tape2010} used SPECFEM3D as well as several additional components which are also stored on the CIG svn server, described next.

>>>>

\newcommand{\nexxi}{\mbox{\texttt{NEX\_XI\/}}}
\newcommand{\nexeta}{\mbox{\texttt{NEX\_ETA\/}}}
\newcommand{\nprocxi}{\mbox{\texttt{NPROC\_XI\/}}}
\newcommand{\nproceta}{\mbox{\texttt{NPROC\_ETA\/}}}
\newcommand{\nchunks}{\mbox{\texttt{NCHUNKS\/}}}
\newcommand{\eg}{e.g.,}

@@

Whatever misfit function you use for the tomographic inversion \citep[several examples in][]{TrTaLi05}, you will weight the sensitivity kernels with measurements. Furthermore, you will use as many measurements (stations, components, time windows) as possible per event; hence, we call these composite kernels ``event kernels,'' which are volumetric fields representing the gradient of the misfit function with respect to one of the variables (\eg $V_{\rm s}$). The basic features of an adjoint-based tomographic inversion were illustrated in \citet{TaLiTr07} using a conjugate-gradient algorithm; there are dozens of versions of gradient-based inversion algorithms that could alternatively be used. The tomographic inversion of \citet{TaLiMaTr09,TaLiMaTr2010} used SPECFEM3D as well as several additional components which are also stored on the CIG svn server, described next.
